Geographically aware estimates of remotely sensed water properties for Chesapeake Bay

### 2022-09-16 manuscript/manuscript.tex
text edits

\FloatBarrier

@@

>>>>

@@

Our data-driven yet geographically aware approach was able to accurately reproduce spatial and temporal patterns of Bay salinity and temperature. In addition to being accurate, our approach provides the ability to generate rapid bay-wide prediction surfaces in seconds and it is easily updatable insofar as saved models can be reloaded and have their training “updated”. Our models are also lightweight with minimal internal complexity and extensively tested against a uniquely large observational dataset.

\subsection{Spatial patterning}

\subsection{Temporal patterning}

\subsection{Future research}
